Networked Character Devices

### 2011-12-12 report/paper.tex
paper: fix so it builds
paper: get the obvious typos. still haven't read through

We did some stuff, we used some references \cite{ldd3}.

@@

Currently we have achieved a successful implementation of the low
level functionality for NCD. The client uses a kernel module written
for linux 2.6.x+ while the server uses a userspace daemon. NCD is
still rough and in need of further development, as it tends to be
crash prone if not treated with care. The groundwork has been laid for
exporting any device, however many device subsystems access their
devices by avoiding the character device interface and these must be
dealt with on an individual basis. Overall, the path for future work
is very clear.

@@

NFS was the first implementation of truely general information sharing
over remote network connections.  However, NFS uses a specific file
system and cannot interface directly with devices.\cite{nfs-source}

NBD (Network Block Device) was included into the linux kernel starting
with version 2.1.101. It enables users to export block devices over the
network, allowing use of any filesystem. However, NBD provides no
exclusive access guarantees and users must acertain on their own
whether the remote drive is being used.\cite{nbd-source}

CUSE (Character Device in User Space) is an extension of FUSE that
allows bringing a characer device into a FUSE filesystem.  This allows
users to access the device directly and potentially export it using
user-level networking.\cite{cuse-article}

USB/IP is a project to share USB devices over IP. This project is
very similar to NCD (as USB devices are character devices) but is
tailored specifinterceptingically to allow sharing USB devices over a
network connection by intercepting USB specific data and encapsulating
it in IP.\cite{usbip-source}

Plan 9 is a distributed operating system developed as a successor to
Unix by Bell Labs.  It implicitly allows sharing devices over a
network via file interfaces. However, plan 9 does not currenty see
wide deployment.\cite{plan9-pike}

@@

% vim: set ts=2 sts=2 sw=2 et spell tw=72 : %
intercepting

>>>>

@@

Currently we have achieved a successful implementation of the low
level functionality for NCD. The client uses a kernel module written
for Linux 2.6.x+ while the server uses a userspace daemon. NCD is
still rough and in need of further development, as it tends to be
crash prone if not treated with care. The groundwork has been laid for
exporting any device, however many device subsystems access their
devices by avoiding the character device interface and these must be
dealt with on an individual basis. Overall, the path for future work
is very clear.

@@

NFS was the first implementation of truly general information sharing
over remote network connections.  However, NFS uses a specific file
system and cannot interface directly with devices.\cite{nfs-source}

NBD (Network Block Device) was included into the Linux kernel starting
with version 2.1.101. It enables users to export block devices over the
network, allowing use of any filesystem. However, NBD provides no
exclusive access guarantees and users must ascertain on their own
whether the remote drive is being used.\cite{nbd-source}

CUSE (Character Device in User Space) is an extension of FUSE that
allows bringing a character device into a FUSE filesystem.  This allows
users to access the device directly and potentially export it using
user-level networking.\cite{cuse-article}

USB/IP is a project to share USB devices over IP. This project is
very similar to NCD (as USB devices are character devices) but is
tailored specifically to allow sharing USB devices over a
network connection by intercepting USB specific data and encapsulating
it in IP.\cite{usbip-source}

Plan 9 is a distributed operating system developed as a successor to
Unix by Bell Labs.  It implicitly allows sharing devices over a
network via file interfaces. However, plan 9 does not currently see
wide deployment.\cite{plan9-pike}

@@

% vim: set ts=2 sts=2 sw=2 et spell tw=72 : %
